\LaTeX\ Author Guidelines for ICCV Proceedings

### 2019-05-09 chapters/5_experiments_noise.tex
Update and move figures

The plots in Fig. \ref{fig:noise_plots} represent the scores achieved by \algname{} with different update rules depending on the amount of noise $\mathcal{K}$ added to the edge weights and the probability $p_{\mathrm{long}}$ of long-range connections in the graph. Results clearly show that adding long-range edges is always beneficial for the final segmentation \TODO{Not True!}. \TODO{What about time?} The most robust version of update rule proved to be the \emph{mean}, that achieves similar scores even with significantly noisy edge weights. The \emph{absolute maximum} update rule proposed by \cite{wolf2018mutex} provides an efficient and fast option, but completely fails when too much noise is added. 
The \emph{sum} update rule version was the slowest option tested, but it was not as robust as the \emph{mean} version, probably due to its tendency to grow one cluster at the time (see Sec. \ref{sec:exp_first_comparison}). \TODO{Comment about MC energy}
On the other hand, \algname{} with \emph{mean} update rule and cannot-link constraints did not achieve high scores because of the strong over-segmentation error.
%Nevertheless, these additional experiments show that it provides an \UPDATE{almost true over-segmentation of the ground truth segmentation even with strongly merge-biased predictions}.

\begin{figure}
        \centering
\begin{minipage}[T]{0.48\textwidth}
% \begin{table}
    \centering
    % \begin{subtable}[t!]{0.5\textwidth}\centering
        \begin{tabular}{l M{0.2\textwidth} M{0.2\textwidth}}
        \toprule
        % & \multicolumn{2}{c}{\thead{Add Cannot-Link Constraints:}} \\
         % & \multicolumn{1}{c}{\thead{\textsc{No}}} & \multicolumn{1}{c}{\thead{\textsc{Yes}}} \\ \midrule
         & \multicolumn{1}{c}{\thead{No\\Constraints}} & \multicolumn{1}{c}{\thead{With\\constraints}} \\ \midrule
         % & \multicolumn{1}{c}{\thead{$\beta$}}  & \thead{AP} & \multicolumn{1}{c}{\thead{$\beta$}} & \thead{AP} \\ \midrule\midrule
\textbf{Mean}& \textbf{0.9292}  & 0.8647  \\
% Lifted multicut & - & -  \\
Abs. Max.  & 0.9246 & 0.9246 \\
Max &   0.0611  &  0.9208  \\
Sum  & 0.8377  & 0.8426  \\
Min &  0.0737 & 0.0779  \\
        \end{tabular}
        % \caption{Linkage criteria}
    % \end{subtable} 
    \captionof{table}{Arand-Scores on CREMI challenge (crop of sample C) \UPDATE{for the generalized algorithm and different types of linkage criteria and the optional use of cannot-link constraints.} }
    \label{tab:results_cremi_val}
\end{minipage}\hfill
\begin{minipage}[T]{0.48\textwidth}
% \begin{table}
    \centering
    % \begin{subtable}[t!]{0.5\textwidth}\centering
        \begin{tabular}{l M{0.25\textwidth} M{0.25\textwidth}}
        \toprule
        % & \multicolumn{2}{c}{\thead{Add Cannot-Link Constraints:}} \\
         % & \multicolumn{1}{c}{\thead{\textsc{No}}} & \multicolumn{1}{c}{\thead{\textsc{Yes}}} \\ \midrule
         & \multicolumn{1}{c}{\thead{No\\Constraints}} & \multicolumn{1}{c}{\thead{With\\constraints}} \\ \midrule
         % & \multicolumn{1}{c}{\thead{$\beta$}}  & \thead{AP} & \multicolumn{1}{c}{\thead{$\beta$}} & \thead{AP} \\ \midrule\midrule
\textbf{Mean}& \textbf{0.343}  & 0.339  \\
GMIS \cite{liu2018affinity} & 0.330 & -  \\
Max &   0.243  &   0.325  \\
Abs. Max.  & 0.321 & 0.321 \\
Sum & 0.313  & 0.319  \\
Min &  0.000    & 0.000  \\
        \end{tabular}
        % \caption{Linkage criteria}
    % \end{subtable} 
    \captionof{table}{AP scores on the cityscapes validation set for the generalized algorithm and different types of linkage criteria.  }
    \label{tab:results_cityscapes}
\end{minipage}
\end{figure}

>>>>

\UPDATE{The plots in Fig. \ref{fig:noise_plots} represent the scores achieved by \algname{} with different update rules depending on the amount of noise $\mathcal{K}$ added to the edge weights and the probability $p_{\mathrm{long}}$ of long-range connections in the graph. Results clearly show that adding long-range edges is always beneficial for the final segmentation \TODO{Not True!}. \TODO{What about time?} The most robust version of update rule proved to be the \emph{mean}, that achieves similar scores even with significantly noisy edge weights. The \emph{absolute maximum} update rule proposed by \cite{wolf2018mutex} provides an efficient and fast option, but completely fails when too much noise is added. 
The \emph{sum} update rule version was the slowest option tested, but it was not as robust as the \emph{mean} version, probably due to its tendency to grow one cluster at the time (see Sec. \ref{sec:exp_first_comparison}). \TODO{Comment about MC energy}
On the other hand, \algname{} with \emph{mean} update rule and cannot-link constraints did not achieve high scores because of the strong over-segmentation error.}
%Nevertheless, these additional experiments show that it provides an \UPDATE{almost true over-segmentation of the ground truth segmentation even with strongly merge-biased predictions}.

\begin{figure}
        \centering
\begin{minipage}[T]{0.48\textwidth}
% \begin{table}
    \centering
    % \begin{subtable}[t!]{0.5\textwidth}\centering
        \begin{tabular}{l M{0.2\textwidth} M{0.2\textwidth}}
        \toprule
        % & \multicolumn{2}{c}{\thead{Add Cannot-Link Constraints:}} \\
         % & \multicolumn{1}{c}{\thead{\textsc{No}}} & \multicolumn{1}{c}{\thead{\textsc{Yes}}} \\ \midrule
         & \multicolumn{1}{c}{\thead{No\\Constraints}} & \multicolumn{1}{c}{\thead{With\\constraints}} \\ \midrule
         % & \multicolumn{1}{c}{\thead{$\beta$}}  & \thead{AP} & \multicolumn{1}{c}{\thead{$\beta$}} & \thead{AP} \\ \midrule\midrule
\textbf{Mean}& \textbf{0.9292}  & 0.8647  \\
% Lifted multicut & - & -  \\
Abs. Max.  & 0.9246 & 0.9246 \\
Max &   0.0611  &  0.9208  \\
Sum  & 0.8377  & 0.8426  \\
Min &  0.0737 & 0.0779  \\
        \end{tabular}
        % \caption{Linkage criteria}
    % \end{subtable} 
    \captionof{table}{Arand-Scores on CREMI challenge (crop of sample C) \UPDATE{for the generalized algorithm and different types of linkage criteria and the optional use of cannot-link constraints.} }
    \label{tab:results_cremi_val}
\end{minipage}\hfill
\begin{minipage}[T]{0.48\textwidth}
% \begin{table}
    \centering
    % \begin{subtable}[t!]{0.5\textwidth}\centering
        \begin{tabular}{l M{0.25\textwidth} M{0.25\textwidth}}
        \toprule
        % & \multicolumn{2}{c}{\thead{Add Cannot-Link Constraints:}} \\
         % & \multicolumn{1}{c}{\thead{\textsc{No}}} & \multicolumn{1}{c}{\thead{\textsc{Yes}}} \\ \midrule
         & \multicolumn{1}{c}{\thead{No\\Constraints}} & \multicolumn{1}{c}{\thead{With\\constraints}} \\ \midrule
         % & \multicolumn{1}{c}{\thead{$\beta$}}  & \thead{AP} & \multicolumn{1}{c}{\thead{$\beta$}} & \thead{AP} \\ \midrule\midrule
\textbf{Mean}& \textbf{0.343}  & 0.339  \\
GMIS \cite{liu2018affinity} & 0.330 & -  \\
Max &   0.243  &   0.325  \\
Abs. Max.  & 0.321 & 0.321 \\
Sum & 0.313  & 0.319  \\
Min &  0.000    & 0.000  \\
        \end{tabular}
        % \caption{Linkage criteria}
    % \end{subtable} 
    \captionof{table}{AP scores on the cityscapes validation set for the generalized algorithm and different types of linkage criteria.  }
    \label{tab:results_cityscapes}
\end{minipage}
\end{figure}
\begin{figure}[b]
\centering
% \includegraphics[width=0.5\textwidth,trim=0.4in 1.2in 0.in 0.05in,clip]{./figs/intro_image.jpg} % left bottom right top
\includegraphics[width=\textwidth]{./figs/cityscapes_compare.pdf} % left bottom right top
\caption{
\UPDATE{Comparison of results from different update rules on signed graph with and without cannot-link constraints}
 \label{fig:cytiscapes_comparison}}
\end{figure}
